\section*{Author Biography}

Ben Payne brings his decades of experience as a professional bureaucrat prior to writing ``Process Empathy: How to be an Effective Bureaucrat."

%Ben Payne %was born in Wisconsin and 
%studied 
As an undergraduate at the 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/University_of_Wisconsin\%E2\%80\%93Madison}{University of Wisconsin}}
\href{https://en.wikipedia.org/wiki/University_of_Wisconsin\%E2\%80\%93Madison}{University of Wisconsin} studying 
Applied Math, Physics, and Engineering, 
Ben was an Air Force National Guard member. He served as a crew chief for 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/General_Dynamics_F-16_Fighting_Falcon}{F-16}}
\href{https://en.wikipedia.org/wiki/General_Dynamics_F-16_Fighting_Falcon}{F-16} jets, deploying to Qatar and Iraq.
%attended  
%for six years, followed by five years at 
%before earning 
He earned his PhD in Physics at the 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/Missouri_University_of_Science_and_Technology}{Missouri University of Science and Technology}}
\href{https://en.wikipedia.org/wiki/Missouri_University_of_Science_and_Technology}{Missouri University of Science and Technology}. Ben joined the 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/United_States_Department_of_Defense}{United States Department of Defense}}
\href{https://en.wikipedia.org/wiki/United_States_Department_of_Defense}{United States Department of Defense} as a federal government employee, where he has been for ten years. While working for the DoD, he taught a graduate-level course on data science for two years at the 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/University_of_Maryland,_Baltimore_County}{University of Maryland}}
\href{https://en.wikipedia.org/wiki/University_of_Maryland,_Baltimore_County}{University of Maryland}. Ben enjoys cooking and traveling. 

