
%See also 
% "Making of a Manager" has Chapter 7 (pages 161-187) on hiring

% https://graphthinking.blogspot.com/2019/06/standard-issues-that-organization-must.html
Voluntary membership in a long-lasting organization implies a turnover rate. Organizations constantly have to onboard new members just to maintain a constant level of membership.

An organization is distinct from the rest of society due to the differences in norms and goals. If an organization does not invest in onboarding, the norms of broader society will prevail. Littering, crime, pollution, scams, and fraud are usually aspects organizations try to constrain.

%In section~\ref{sec:hiring} 
\hyperref[sec:hiring]{Hiring}\iftoggle{haspagenumbers}{ (see page~\pageref{sec:hiring})}{}
is discussed from the perspective of the person hiring and the person being hired. 
%In section~\ref{sec:promotion} 
Incentives for \hyperref[sec:promotion]{promotion}\iftoggle{haspagenumbers}{ (see page~\pageref{sec:promotion})}{}
are described from the view of the person promoting a bureaucrat and the person seeking promotion. 
%In section~\ref{sec:professional-training} 
%I explain the relevance of \hyperref[sec:professional-training]{professional training}
%\marginpar{See page~\pageref{sec:professional-training}}
%from the perspective of the employer and the employee. 
The reason to cover both roles is to help people in each position build empathy with the other person's experience. 


\section{Hiring into a Bureaucracy\label{sec:hiring}}


Hiring shapes the culture of an organization and determines what is feasible, both by the skills of those hired and how well new hires integrate with the existing organization. 

Hiring is an expensive process in terms of money, time, emotional investment of candidates, and the burden of reviewing applicants. 
% TODO: SO WHAT? What's the consequence?
As a candidate, recognize the risk the organization is taking. 
As a reviewer of candidates, this is an investment in the future of the organization. Even if your bureaucratic role does not require an exclusive focus on hiring, there is value in studying this domain. 

%When hiring into an organization 
There is a \href{https://en.wikipedia.org/wiki/Selection_bias}{selection bias} in
\index{Wikipedia!selection bias@\href{https://en.wikipedia.org/wiki/Selection_bias}{selection bias}}
the people who join a bureaucratic organization, and there is a selection bias to who stays in a bureaucratic environment. 
% TODO: SO WHAT? What's the consequence?
The people in a bureaucratic organization are not representative of the society that the organization serves. Tactics that work inside a bureaucratic organization may not apply more generally, and tactics that are useful outside an organization may not work on bureaucrats. 


% https://leadership.garden/onboarding-engineers/
% https://news.ycombinator.com/item?id=30810786

Regardless of the role, there are specific attributes that make a candidate more likely to be successful in a bureaucracy. In addition to role-specific skills, hire for the ability to reflect on thinking (\href{https://en.wikipedia.org/wiki/Metacognition}{metacognition}),
\index{Wikipedia!metacognition@\href{https://en.wikipedia.org/wiki/Metacognition}{metacognition}}\iftoggle{WPinmargin}{\marginpar{$>$Wikipedia: Metacognition}}{}
navigating complex social scenarios with competing interests, and intrinsic motivation.

% https://graphthinking.blogspot.com/2021/04/screening-for-metacognition-in-job.html

% https://graphthinking.blogspot.com/2021/07/screening-for-intellectual-empathy-in.html

% https://graphthinking.blogspot.com/2021/04/questions-to-ask-interviewer-when.html

