\subsection*{Changing your Environment}

% https://quoteinvestigator.com/2017/05/23/culture-eats/
%\begin{quote}
%    Culture Eats Strategy for breakfast
%\end{quote}
%\href{https://en.wikipedia.org/wiki/Peter_Drucker}{Peter Drucker}

Changing the bureaucratic organization you are a member of is difficult. That applies regardless of your motive for change and the thing to be changed. Regardless of motive, there are tactics applicable to any change. 
The two major categories of change are 
\marginpar{See page~\pageref{sec:change-a-process}.}%
\hyperref[sec:change-a-process]{processes} (e.g., technical solutions, changing policy)
%\ifsectionref
%described in section~\ref{sec:change-a-process} 
%\fi
and changing the \gls{culture} of the members of an organization.
%\iftoggle{glossaryinmargin}{\marginpar{[Glossary]}}{}%

\ \\

\iftoggle{glossarysubstitutionworks}{\Gls{culture}}{Culture} is the set of norms that determine acceptable behavior for members of the organization. Norms are the expectations of your fellow bureaucrats. Each member of the organization can model desired behavior and inflict punishment for deviation from norms. The culture of the organization is practiced by members. 

% https://graphthinking.blogspot.com/2021/01/why-active-shaping-of-culture-is.html
The expectations of an organization should be stated explicitly so that members cannot use the defense that they were not aware. If the stated norms conflict with what is experienced by the organization's members and left unaddressed, the hypocrisy decimates trust. 

Besides modeling desired norms in the organization, there are a few more tactics you can take. 
\marginpar{$>>$ Actionable Advice}
\index{actionable advice}
You can reinforce examples of desired behavior with public praise and meaningful rewards. You can counsel people who go against the culture and punish instances of undesirable norms. 

Altering the culture of an organization means altering member behavior and expectation. This is accomplished by adjusting incentives to reinforce the desired behavior, punishing undesirable behavior, and providing resources to make the intended outcomes easier. 

Although aspects of culture may be problematic, thinking of cultural change as problem-solving can be a misleading framing. Rather than solve problems think of change as addressing challenges. %The word ``problem" implies a solution. 
Altering the culture often introduces novel challenges.
%The problem-solution framing is ina since . 
Even though you don't solve a challenge, you can still get a sense of emotional reward from having improved the situation. 

\ \\

Before investing effort in change, reflect on the emotional and career impact of your effort. Will the work bring you joy, or is your emotional reward tied to the outcome? If the outcome is the only source of reward, you'll either be disappointed in failure or you will be more conservative (intending to increase the likelihood of success). The work of creating positive change can be joyful: you can form relationships and focus on learning. 

One of the challenges of change in a bureaucratic organization is figuring out what is worth changing. There are many opportunities for improvement. Talk to stakeholders and enumerate their challenges.
\marginpar{$>>$ Actionable Advice}%
\index{actionable advice}%
From the myriad stories, identify recurring themes and root causes. Typically bureaucratic challenges intertwine technical, budget, staffing, historical context, personalities of participants, and organizational politics. 

Select an aspect that you have some competence in and would facilitate personal growth. If the challenge is big (many people involved, takes a long time, costs a lot), can it be broken down into incremental challenges? Distinguish wide-scale changes you envision from local changes over which you have more influence.

Having surveyed challenges worth addressing and having picked an issue with a high return on investment, the guidance of
\href{https://en.wikipedia.org/wiki/G._K._Chesterton\%23Chesterton\%27s_fence}{Chesterton's fence}
\index{Wikipedia!Chesterton's fence@\href{https://en.wikipedia.org/wiki/G._K._Chesterton\%23Chesterton\%27s_fence}{Chesterton's fence}}%
\marginpar{$>>$ Folk Wisdom}%
\index{folk wisdom!Chesterton's fence@\href{https://en.wikipedia.org/wiki/G._K._Chesterton\%23Chesterton\%27s_fence}{Chesterton's fence}}%
\iftoggle{haspagenumbers}{(page~\pageref{concept:chestertons_fence})}{section~\ref{concept:chestertons_fence}} 
is that you shouldn't change something until you understand why things are the way they are. Figuring out the history of an issue requires work when there is a lack of historical records.

Talking to stakeholders in the survey phase may yield tidbits of history. Why have previous efforts been rejected or not taken effect? Your review of written documentation of the history should be augmented by seeking out oral folklore. 

If your idea has a novel justification for success, identify all possible methods of progress and then rank the tasks. If you can't do all the work, who can you collaborate with? Can you delegate to people with skills you lack, or will you have to gain new skills? 
If no one has the relevant skills, becoming the widely-acknowledged expert improves your influence. 


