\section{Communication Preferences\label{sec:communication-preferences}}
% why this matters: source of friction among bureaucrats
% benefit to reader: understanding why people are different

There are typically multiple communication channels available between bureaucrats in an organization. Rather than focus on specific implementations using specific technologies, consider two variables. The first variable is asynchronous versus synchronous. Examples of asynchronous communication channels include voice mail, email, web forums, websites, and calendars. Synchronous options include phone calls, video calls, in-person, text-based chat like \href{https://en.wikipedia.org/wiki/Internet_Relay_Chat}{IRC}
\index{Wikipedia!IRC@\href{https://en.wikipedia.org/wiki/Internet_Relay_Chat}{IRC}}
or \href{https://en.wikipedia.org/wiki/Slack_(software)}{Slack}. \index{Wikipedia!Slack@\href{https://en.wikipedia.org/wiki/Slack_(software)}{Slack}} 
The distinction between asynchronous and synchronous can be blurred, like if someone immediately replies to your (asynchronous) email.  The second variable is a set of categories: voice (e.g., phone), text (e.g., website, web forums, calendars), video (e.g., calls), and in-person. 

The two variables are  latency (how much delay) and bandwidth (how much content per unit time). Any novel communication technology, platform, or service is characterized by latency and bandwidth. 

% https://graphthinking.blogspot.com/2016/04/communication-channel-equivalence.html
When a communication channel has less bandwidth, there is a loss of ability to interpret intent. 
For example, consider audio that has been converted to text. In addition to the text transcription, voice audio  has inflection, volume, volume variation, rate, and rate variance. Those aspects help the audience understand the speaker better, improving the effectiveness of communication.

The relevance to a bureaucrat of identifying these channels is to know which channel is preferred for what purpose.  You can list your preferences so that people know how best to engage with you.
\marginpar{$>>$ Actionable Advice}
\index{actionable advice}
Second, you can learn and then leverage the preferences of people you collaborate with.
\marginpar{$>>$ Actionable Advice}
\index{actionable advice}

As an example of knowing your behaviors, do you keep your calendar up-to-date? Or is your calendar irrelevant? Is that preference stated explicitly to the people who might reference your calendar? Is your calendar visible to your coworkers?

\ \\

The following illustrates when to use which channel for what purpose, and in what order. 

Text chat is useful for asynchronous interrupts. Text chats are better than stopping by in person or calling on the phone since in-person drive-bys and phone calls interrupt whatever I'm thinking about or discussing. The purpose of the text chat is either a reminder or to find a convenient time to talk. 

Email is useful for notifications or questions or setting up logistics. If I don't respond to your question or request for action within two days, please send a reminder. 

Video calls are my preferred method for group meetings. Group meetings via video call scheduled in advance on my calendar are best. Impromptu video calls are acceptable but as disruptive as a phone call. 

In-person discussions are my preferred method for one-on-one discussions. Stopping by my desk  without an appointment interrupts whatever I'm thinking about. If a calendar invitation is inconvenient, a text chat confirming my availability before the in-person discussion is helpful. 

The phone is useful when the caller is unable to be present in-person. Phone, being voice-only, is inferior to video calls. Unscheduled phone calls interrupt whatever I'm thinking about. I've intentionally disabled voicemail. 

Status updates in electronic issue trackers, wikis, or forums are best (rather than email-only). Notifying in text chat or email that a wiki page or issue is updated is helpful but not mandatory. 

Given all those caveats, I prefer communication in any form at any time over surprises. 

If you're unsure whether you should communicate, default to communicating. If you're not sure whether communication would interrupt something, check my calendar and then communicate. If it's urgent or blocking progress, ignore my calendar and interrupt me. 

\ \\

You may not have the same prioritization, or you may not have as detailed preferences. The take-aways from the above example are that you should know when to switch communication channels.
\marginpar{$>>$ Actionable Advice} 
\index{actionable advice}
You should know when to start in one channel and then escalate from text to phone to in-person.

\ \\

% TRANSITION from preferences to communication_vulnerability

The discussion above of which channel to use is person-specific. While bureaucracy can seem (and is designed to be) impersonal, being an effective bureaucrat means tailoring your interactions to the people you work with. That personalization doesn't have to stray into being intimate friends; there's a professional capacity for vulnerability. 