\section{Dilemmas and Trilemmas\label{sec:dilemma_trilemma}}

A simple decision is one that has one good choice and one or more bad choices. Then the goal is to identify which is the good choice and select that option.

A complex decision may have many choices, and there are might not be a best option. Then a Pareto frontier might exist where trade-offs can be made. 

When a decision has two viable options, that presents a \href{https://en.wikipedia.org/wiki/Dilemma}{dilemma}. The name for the case with three viable options is a \href{https://en.wikipedia.org/wiki/Trilemma}{trilemma}.

Dilemmas create cognitive dissonance

The following are presented as dilemmas, but that oversimplifies both the continuous nature of the trade-off and the alternative creative approaches to a specific solution. The reason to be aware of these dilemmas to be able to ponder them prior to the pressure of real-time decision making. 

\ \\


\textbf{control via rules versus freedom/autonomy/agility} aka
\textbf{Number of rules: high versus low}:\\
The more rules that exist the more likely it is that someone will find a way to exploit them to their own advantage.
The fewer rules that exist the more likely it is that someone will try to get away with something bad


\ \\

\textbf{Speed of task completion: fast versus slow}:\\
Do a task quickly (and perhaps ineffectively or inefficiently or even wrong) versus taking time to do the task right (with opportunity cost).

Methodical well-planned design towards getting the right solution versus implementing a solution quickly to address urgent needs


\ \\

\textbf{How much data to gather for a decision: a lot or a little}:\\
Knowing what to do versus the cost of observability. Collecting data is expensive. Lack of data results in decisions based on oversimplified assessment

\ \\

\textbf{how much data to publish: less or more}:\\
publishing data cost resources (people, money, time). Publishing data improves transparency and accountability. Restricting data access saves money for the data owner and improves flexibility. 

\ \\


\ \\

\textbf{Scope of impact: broad versus narrow}:\\
Niche impact means less politics

\ \\

\textbf{staffing flexibility versus efficiency}
Have a small amount of staffing versus cover all edge cases (resilient to changing demands by having slack resources). A smaller, centralized government is less costly, but also less sensitive to local issues. 

bureaucratic inefficiency, or spare capacity that enables resilience to change?
Efficient can be fragile is requirements change


\ \\

\textbf{services that are necessary but not central: in-house versus external dependency}:\\
for non-central services required by the organization, in-house versus outside provider. In either case, the organization is screwed.

\ \\

\textbf{Decision making in a hierarchy: lower versus higher}:\\
the higher up a decision is made, better scope and the decider will have. That decider will have less skin in the game and be less well informed. Pushing decisions down means more inconsistency

\ \\

\textbf{Services within an organization: redundant market versus monopoly}: \\
redundant services to choose from to enable customers to choose the best service (using a market model within the organization) versus efficiency of a single service which might not meet the needs of all customers

solution A exists but doesn't meet my needs. 
rather than tweak A, re-invent solution B which mostly overlaps with A but has independent development and support. 


\ \\

\textbf{choose fast inexpensive good}

\href{https://en.wikipedia.org/wiki/Project_management_triangle}{Project management triangle}