% https://graphthinking.blogspot.com/2021/02/how-to-have-efficient-bureaucracy.html

\section{Efficient Bureaucracy}

In an ideal scenario with no bureaucracy, everyone comes to the same conclusion when presented with the same information. Then the management process of building consensus becomes unnecessary. There is no need to fight over resources (money, staffing) and no need to fight over direction.

While that ideal scenario is not going to happen, it points to how to improve bureaucratic efficiency:
\begin{itemize}
\item each person has the same information. 
\item each person applies the same decision making process consistently
\item every person has the same incentives
\end{itemize}
The reason bureaucracy is inefficient is
\begin{itemize}
    \item not everyone has the same information
    \item processes are inconsistent
    \item incentives vary
% https://graphthinking.blogspot.com/2017/03/what-slows-down-bureaucracy.html
    \item Imprecise language
    \item Using opinions and experience rather than collect data and analyze data
    \item prioritizing by putting out fires rather than attacking largest issues
    \item not responding to communications (email, phone, meetings)
    \item being late to meetings
    \item scope creep
    \item planned scope and capability scope (due to staffing or skills) is mismatched
    \item silos of operation
% https://graphthinking.blogspot.com/2017/03/progress-in-spite-of-better-ways.html
    \item lies
    \item mistakes
\end{itemize}
Also, add the issue that each person's reference experiences are unique. As a consequence, decision making is subjective. 



Can any action be taken to improve bureaucratic efficiency? Yes!
\begin{itemize}
\item you can share information with other stakeholders
\item you can seek information from other stakeholders
\item you can strive for and demonstrate transparency
\item apply consistent processes (rather than being reactionary and applying ad hoc responses)
\item hold others (and yourself) accountable 
\item account for varying incentives and reference experiences
\end{itemize}
