\section{Fundamentals of Bureaucracy\label{sec:fundamentals-of-b}}

There are four essential elements of bureaucracy: a shared resource and three roles (policymaker, bureaucrat, subject) inhabited by different people. 
These elements give rise to observable features that are commonly cited as being bureaucratic, but these aspects are referred to here as Fundamentals of Bureaucracy.
This section outlines the critical roles of decision-making, hierarchy, communication in bureaucracy, and feedback loops. 
% the following sentence acknowledges there's a difference but doesn't explain why there's a difference.
The list presented here is smaller than \href{https://en.wikipedia.org/wiki/Bureaucracy\%23Max_Weber}{Max Weber}'s~\cite{2015_Weber}.
\index{Wikipedia!Weber, Max@\href{https://en.wikipedia.org/wiki/Bureaucracy\%23Max_Weber}{Weber, Max}}
% and I see bureaucracy as more widespread.

\hyperref[sec:decision-making]{Decision-making}
\marginpar{See page~\pageref{sec:decision-making}.}%
%\ifsectionref
%(section~\ref{sec:decision-making}) 
%\fi
is central to bureaucracy. Every other aspect of bureaucracy derives from decision-making. 
%Bureaucracy is a system of distributed knowledge and distributed decision-making for managing shared resources. The decision-making is not purely logical; it relies on particular facets of human interaction. 
The decision-making in bureaucracy is for the management of access to shared resources. In the definition of bureaucracy used in this book, ``\iftoggle{glossarysubstitutionworks}{\glspl{shared resource}}{shared resources}'' 
\iftoggle{glossaryinmargin}{\marginpar{[Glossary]}}{}%
refers to information, expertise, and tangible goods. %like air, water, and land. 


%or even when one person is trying to be self-consistent, 
Coordination of decision-making is crucial to the management of shared resources when there are multiple people participating. Who gets to make which decision is managed using a
\hyperref[sec:hierarchy-of-roles]{hierarchy} of roles.
\marginpar{See page~\pageref{sec:hierarchy-of-roles}.}%
%\ifsectionref
%; see section~\ref{sec:hierarchy-of-roles}.
%\fi
While coordination can occur without hierarchy when there are a small number of people, typically an organization of people leads to both formal and informal hierarchies. 

\hyperref[sec:meetings-for-coordination]{Meetings} and 
\marginpar{See page~\pageref{sec:meetings-for-coordination}.}%
\hyperref[sec:written-communication]{written communication} help with consensus among bureaucrats, though agreement isn't necessarily the outcome.
Once a decision is made, the choice selected by a bureaucrat propagates throughout the organization to achieve some level of consistency. 

A less prominent feature of bureaucracy is the weak 
\gls{feedback loop}. 
 \iftoggle{glossaryinmargin}{\marginpar{[Glossary]}}{}%
 This distinguishes bureaucracy from a market-based system where the consequences of decisions manifest as profits and losses. If you sell shoes, you can evaluate decisions you've made by measuring how much money you make. In contrast, the decisions of a bureaucrat are often barely felt by the bureaucrat. That weak feedback loop (few consequences for the decision-maker) means learning from mistakes is harder and positive reinforcement for good outcomes is negligible. A weak feedback loop does not mean there are no consequences. The actions of a bureaucrat create ripples that other people feel. This is described in more detail in the section on \hyperref[sec:feedback-loop-and-ripples]{feedback loops and ripples}.
\marginpar{See page~\pageref{sec:feedback-loop-and-ripples}.}

%\ \\

If you're not an academic researcher of bureaucracy, you might not want to think about hierarchy, collaboration, or coordination. 
Meetings and email are not your goal; you just want to do the tasks you are trained for. This attitude is consistent with your experience in school where you progressed by being graded as an individual student. Now that you are employed your job has pay, promotion, hiring/firing, and a title. School, and now employment, may seem focused on your abilities (instead of on the class you're in or the team you're a member of). While this attitude is common, it is not effective.

The following sections explain why the individualist mentality is ineffective when you are part of a system of distributed knowledge and distributed decision-making. 


% there are examples where the ability of the team is measured: 
% An example of hiring a team is when a company buys another company for talent acquisition.