\section{Leveraging Expertise\label{sec:expertise}}

%**************************************
% Generic observations on Expertise
%**************************************

The definition of \gls{bureaucracy} is the management of shared resources on behalf of a community. In addition to tangible shared resources like land, water, and air, an intangible resource accessed by a community is expertise. Bureaucrats are responsible for finding people with expertise, vetting claims of expertise, and deploying expertise for the benefit of a community. 

Experts who accumulate knowledge and experience look for ways to apply their expertise. Finding the relevant decision-makers and providing context for decisions can feel satisfying when positive  outcomes benefit a community. 


The following two sections address both viewpoints: that of a bureaucrat seeking expert help, and that of an expert providing input. Bridging the cultural divide and knowledge gap in both directions is necessary for the success of an organization.

\subsection*{Non-experts seeking Experts}
%*******************************************************
% Advice for Bureaucrats collaborating with Experts
%*******************************************************

Before you seek the help of an expert, your first instinct may be to try and proceed on your own. \textit{How hard could this be? Looks straightforward enough...} That do-it-myself approach is a plateau you can remain on for an entire career. Or perhaps you encounter difficulties and realize your limitations. You may seek help from a local peer. Seeking help from those around you is a second plateau that may suffice for the issue you're responding to. When local knowledge is inadequate you need an expert.

Finding an expert can be difficult to distinguish from talking with non-experts who know something you don't. If you decide a challenge requires skills you don't have, anyone with those skills has more expertise than you. Expertise is relative. 

\subsubsection*{Finding Experts}

One reason you as a bureaucrat seek an expert is you don't have expertise yourself. (If your motivation is merely to seek an external scapegoat that can be blamed, then getting any expert that appears convincing will suffice.)

A technique for finding a relevantly qualified expert is to triangulate. 
\marginpar{$>>$ Actionable Advice}%
Seek guidance from your existing social network. Multiple referrals from independent parties are a positive indicator. That is not the same as vetting the person's claimed expertise.

Once you've identified a potential expert, you'll need to evaluate their expertise and the ability to collaborate. This is inherently difficult since you lack the expertise you are seeking.

Do people defer to the candidate because of the candidate's title, the candidate's position in the hierarchy, the candidate's experience, or the candidate's knowledge of technical details? Those can each qualify someone as an expert, but the title and position are least connected with expertise. Even experience can be misleading: ten years of doing a job can sometimes mean just doing the same first-year activities for ten years. %Formal education can serve as a signal of expertise, but practical experience is 
Evaluating an expert's depth of insight is often relegated to peers in the same field. 

 

When signaled solely by credentials, expertise is independent of experience. Another risk is that the expert may lack the ability to communicate their knowledge with people outside their domain.

Within an area of expertise there may be sub-disciplines that you are not familiar with. Don't be embarrassed to ask the expert you find what subfield they have experience in, and their evaluation of how well that aligns with the effort you're recruiting them for.

%\begin{itemize}
%    \item When asked about the topic, does the candidate respond defensively (emotionally) or with an anecdote or with a direct answer (logical)?
    %\item Does the candidate know the history of the topic? The important people in the field? The history matters for understanding the evolution of mistakes and innovations of the topic.
 %   \item Does the candidate know who the stakeholders are for the current situation? 
%\end{itemize}


\subsubsection*{Communicating with Experts}
A common barrier to successful collaboration is the use of jargon by experts.
Jargon can serve two purposes: to signal group membership (which is harmful to people outside the group), and to be more precise about a concept (a desirable trait). A pseudo-expert may use jargon relevant to a topic but not be able to explain the concept to you. That can be indistinguishable from someone who does know but explains poorly.

If you're tackling a complex challenge, you may need experts from different disciplines. This introduces added challenges of cross-discipline communication. 

As a way of distinguishing people who know more than you do, consider the following levels of expertise.
\begin{enumerate}
    \item A self-designated expert is unfamiliar with domain-specific jargon.
    % Does the candidate use the relevant jargon for the topic?
    \item A pseudo-expert can use jargon in discussion but cannot expand the definition or provide analogs.
    % Does the candidate use the jargon for the topic in the right way?
    \item A pseudo-expert has memorized definitions and can use analogies but doesn't grasp underlying relations and principles. Boundaries of what to apply where are uncertain.
    \item An expert can map the situation-of-interest to underlying relations and principles, then use that mapping to remedy the issue (or explain why a fix is infeasible). The result works and the solution wasn't obvious to non-experts.
    % Can the candidate explain the topic with minimal use of jargon?
\end{enumerate}

For bureaucrats seeking to leverage experts, there is the confusing use of caveats. People who don't have a depth of knowledge are more likely to be overconfident, while people who do have expertise are cautious about including caveats and limitations.\footnote{See Wikipedia entry on the \href{https://en.wikipedia.org/wiki/Dunning\%E2\%80\%93Kruger_effect}{Dunning-Kruger effect}.
\index{Wikipedia!Dunning-Kruger effect@\string\href{https://en.wikipedia.org/wiki/Dunning\%E2\%80\%93Kruger_effect}{Dunning-Kruger effect}}
}

%\subsubsection*{What to use an Expert For}

%Translation process is necessary from ``here's what's known in general" + ``situation specific facts" to ``plan of (in)action" and what's realistic with what confidence. 

%Experts straying outside their expertise are dangerous because the boundary may not be clear to the audience.


%***************************************************
% Advice for Experts collaborating with Bureaucrats
%***************************************************

\subsection*{For Experts Looking to Help Non-expert Decision-makers}

Providing help to decision-makers can be an emotionally rewarding application of your skills. The interaction with bureaucrats can also feel devastating when you aren't listened to, you aren't understood, or your input is perverted in ways you didn't want. %The relationship you have with the decision-maker 
Identify strengths your audience has and build on those.

%\subsubsection*{Finding the relevant person to provide advice to}

%\subsubsection*{How to talk with non-experts}

%Coherence of data can lead to increased confidence about the results.
%Having less data may be more coherent. 

%More data is likely to be less consistent and therefore lowers confidence.

%Non-experts think and speak less precisely.

%You will need to simplify in the sense of applying to the relevant decisions - funding, staffing, planning.


% https://graphthinking.blogspot.com/2012/05/notes-on-consulting-experience.html
You, the expert, may not win any debates based on the number of years of experience. Some audiences may have many years in the field. However, expertise (rather than experience) is what they can benefit from. 

To establish boundaries on advice-giving, identify areas in which you have specialized knowledge and which areas  the non-expert audience has insights that you do not.
Respect and account for the expertise of the audience (especially when they work in a different field). Acknowledge your  limits and account for their limits.

Instead of relying on providing expertise as a single-dimensional relation, find ways to relate personally to audience members. The purpose of creating and maintaining a personal relationship is necessary because they will need to trust you.

%Facilitate the audience setting the goals. They should be able to identify how success is defined.

When you have multiple people seeking to learn from your expertise you don't have to teach the group all at once. You can provide one-on-one teaching in which the audience may feel less worried about asking dumb questions.
Once you've taught more than one person, they can help each other translate the insights. 

%\subsubsection*{Advice for Experts}

Being the sole subject matter expert in an organization can feel isolating. You are constantly educating others, but the stakeholders are not expected to become your peers. Typically stakeholders want to know just enough to make a decision. 

%You should explicitly acknowledge to your audience that expertise is relative. 

When there are no other experts locally available who you can ask questions of, turning to membership in professional organizations is an option.

Lastly, there is a risk that your expertise is crucial to the decision-maker. That dependence can result in you thinking that you are important, but it also means the decision-maker will be less successful if you are unavailable. You should invest in cultivating your replacement. 
\marginpar{$>>$ Actionable Advice}