\documentclass{book}
% to set font size use
% \documentclass[12pt]{book}

% https://www.overleaf.com/learn/latex/Tables
\usepackage{array}
\newcommand{\dilemmatablewidth}{5.5cm}


\usepackage{graphicx}

% https://www.quora.com/What-font-are-most-books-printed-in
% to set font, use
%\usepackage{ebgaramond}

\usepackage{hyphenat} % http://www.ctex.org/documents/packages/special/hyphenat.pdf

\usepackage{setspace}\onehalfspacing\frenchspacing\flushbottom\sloppy

% https://www.scivision.dev/include-svg-vector-latex/
%\usepackage{svg}
% see https://tex.stackexchange.com/questions/442077/is-it-possible-to-use-svg-images-with-overleaf

% https://tex.stackexchange.com/a/8459/235813
\usepackage[nottoc]{tocbibind}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

% https://en.wikibooks.org/wiki/LaTeX/Glossary says
% "\usepackage{glossaries} and \makeglossaries in your preamble (after \usepackage{hyperref} if present)"

% https://www.overleaf.com/learn/latex/Glossaries
\usepackage[toc]{glossaries}
%\usepackage{glossaries-extra}

\makeglossaries % The command must be before the first glossary entry.

% https://en.wikibooks.org/wiki/LaTeX/Glossary says
% "define any number of \newglossaryentry and \newacronym glossary and acronym entries in your preamble"
\input{glossary_entries}

\title{How to be an Effective Bureaucrat\\
A Field Guide}
\author{Ben Payne}
\date{\today}

\begin{document}
\pagenumbering{alph} % Fixes problem with glossary links; see https://tex.stackexchange.com/questions/119527/glossary-backlink-points-to-wrong-page

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}
\newpage

%\thispagestyle{empty}
\frontmatter % the front of the book has roman numerals

%\pagenumbering{gobble}
\input{copyright}\clearpage
\input{dedication}%\clearpage
%\pagenumbering{roman}

\chapter*{Foreword}% * excludes from Contents)
\input{foreword}%\clearpage

\hypertarget{contents}{}
\tableofcontents

\mainmatter % the main part of the book will have standard pages

% https://tex.stackexchange.com/questions/2958/why-is-newpage-ignored-sometimes

\chapter{Introduction to Bureaucracy}
% essentials

  \input{what_is_bureaucracy}\newpage % section
  \input{alternative_views_of_bureaucracy_from_within}
  \input{models_of_bureaucracy}\newpage % section

  \section{Fundamentals of Bureaucracy\label{fundamentals_of_b}}
  
  This section provides terminology and definition for a bureaucratic lens. Specifically bureaucracy is defined and labels for roles in bureaucracy are named. Structure in organizations is often characterized by hierarchy, and that hierarchy is described by an ``organization chart.'' Lastly, meetings and written communication are the way in which consensus among bureaucrats is established.

    % define the core concepts 
    \input{hierarchy_of_roles_in_bureaucracy}
    \input{org_chart_as_guide_and_as_lie}
    \input{not_many_options_for_organizations}
    \input{meetings_for_coordination}
    \input{written_communication} % this isn't essential, just common
    \input{decision_making}
    \input{feedback_loops} % subsection
  \newpage
  \input{history}\newpage % section
  \section{Scope of bureaucracy}
  %\begin{flushright}
  %Back to the \hyperlink{contents}{Table of Contents}
  %\end{flushright}
    \input{who_is_a_bureaucrat} % subsection
    \input{number_of_people_in_a_bureacracy} % subsection
    \input{why_does_bureacracy_exist} % subsection
    \input{why_is_bureaucracy_hard}
  %\input{from_startup_to_bureaucracy}

\chapter{Bureaucracy in general}
  \input{phases_of_life} \clearpage
  \input{avoiding_bureaucracy_is_nearly_impossible} \clearpage
  %\input{folk_wisdom}\clearpage
  \input{accidental_and_essential_bureaucracy}\clearpage
  \input{fallacies} \clearpage
  \input{dilemmas_and_trilemmas} \clearpage
  \input{unavoidable_hazards} \clearpage
  \input{effective_bureaucrat} \clearpage

\chapter{Bureaucracies are made of Humans\label{b_made_of_humans}}
% instead of presenting specific lessons, here I'm going to present insider perspectives on the fundamentals described in previous chapters. 

This chapter provides an insider's perspective of working in a bureaucracy. What are all the aspects to consider?
% unordered essays to be clustered later

  \section{Getting started in a Bureaucracy}
    This section focuses on a bureaucrat's initial exposure to bureaucracy. 
  
    \input{what_to_read}
    \input{hiring}
    \input{promotion}
    \input{org_chart_orientation}
    \input{professional_training}
  \newpage
  \section{You are an Individual in an Organization}
  
    This section focuses on the individual bureaucrat operating within an organization. 
    
    There is no neutral member of a bureaucracy. Either you are contributing to the organization, or you are sapping resources from the organization. This is because the organization operates in a zero-sum game for resource allocation.
    \input{ideas_for_innovation}
    \input{motivations_of_participants}
    % management isn't leadership
    \input{creating_change}
    \input{measures_of_maturity}
  \newpage
  \input{working_with_other_bureaucrats} % section
    \input{not_my_job_task_scope}
    \input{building_managing_spending_reputation}
    \input{teams}
    \input{leveraging_expertise}
        \input{does_anyone_want_to_volunteer}
  \input{internal_product_development_deployment}
  \newpage
  \input{processes}
    \input{approval_forgiveness_opposition} % subsection
    \input{static_vs_dynamic_processes}
    \input{bureaucratic_debt} %subsection
    \input{design_processes_for_turnover}
    %\input{processes_tax_productivity}
  \newpage
  \section{Communication within a Bureaucracy}
  I don't want to talk specifically about paper memos versus email versus phone calls versus video chat versus Skype versus slack. 
The relevant attributes are synchronous versus asynchronous. Searchable or not searchable. In that context, there might be some interesting bureaucratic specific things to think about
    \input{role_of_communication}
    \input{communicate_failure_to}
    \input{communication_preferences}
    \input{communication_within_bureaucracy}
    \input{social_and_bureaucratic_interactions} % subsection
    \input{communication_techniques} % subsection 
    \input{friction_between_teams_within_organization}

    %There are many books on how to do meetings well. 
    % How is this section (in a book about bureaucracy) distinct?
    % how does understanding bureaucracy matter in the context of a meeting? what's the change in behavior for the effective bureaucrat?
    Stakeholders care about the outcome of a decision. 
    In some sense, every participant in an organization is invested the outcome of every decision made because there is consequence to how resources are allocated and the direction of the organization. Every org member has an opinion, even lacking experience or expertise. 
    
    \input{well-run_meeting}
    \input{characterizing_meetings}
%    \input{make_effective_presentations}
    % how to engage your audience
    % stages of dysfunction
%    \input{meeting_time_versus_theft}
    
    \input{one-on-ones}
%    \input{conference_attendee}
%    \input{conference_organizer}

\chapter{Last chapter}
\input{last_chapter}

% If bureaucracy is a distributed knowledge distributed decision system, compare with paxos and Byzantine generals
% https://en.wikipedia.org/wiki/Paxos_(computer_science)
%https://blog.the-pans.com/understanding-paxos/
%https://martinfowler.com/articles/patterns-of-distributed-systems/paxos.html

% https://en.wikipedia.org/wiki/Complexity_theory_and_organizations


\appendix

\chapter{Assessments for Publication}
\input{readers_report}\newpage % section
\input{audience_analysis}\newpage  % section

\chapter{Book notes}
\input{book_notes/blau_dynamics_of_bureaucracy}\newpage
\input{book_notes/dugay_values_of_bureaucracy}\newpage
\input{book_notes/farazmand_handbook_of_bureaucracy}\newpage
\input{book_notes/graeber_utopia_of_rules}\newpage
\input{book_notes/hupe_research_handbook_on_street-level_bureaucracy}\newpage
\input{book_notes/lipsky_street-level_bureaucracy}\newpage
\input{book_notes/ohearn_bureaucrats_handbook}\newpage
\input{book_notes/vine_bureaucracy_a_key_idea_for_business_and_society}\newpage
\input{book_notes/vonmises_bureaucracy}\newpage
\input{book_notes/wilson_bureaucracy}


\clearpage

\printglossaries

\nocite{*} % causes LaTeX to include every entry in your .bib file.

% http://www-math.ucdenver.edu/~billups/courses/guides/annotated_bibliography.html
\bibliographystyle{plain-annote}
\bibliography{biblio_bureaucracy}%,biblio_meetings}

\end{document}
