\section{Motives of Bureaucrats\label{sec:motivations}}

Learning the diverse motives of bureaucrats you depend upon is instructive for finding causes of delay or opposition. If you expect everyone to have the same motives as you, then you will be surprised by the friction created by diverse motives. 

Motivations of participants are rarely, ``How can I make the organization more successful?" or even, ``How can I sell or produce more product?" Usually, motivation is based on personal fulfillment in various manifestations. Learning the motives of each bureaucrat - what they value in terms of a \href{https://en.wikipedia.org/wiki/Utility}{utility function}
\index{Wikipedia!utility function@\href{https://en.wikipedia.org/wiki/Utility}{utility function}}
and how they perceive risk - enables you to gather data that is personally relevant to the argument you're making and frame your narrative more effectively.


Bureaucrats on the same team with similar skill sets have similar external incentives. However, their intrinsic motives may be different and result in distinct behaviors. Within an organization, bureaucrats differ due to their intrinsic motivations,  extrinsic incentives, and each person's risk tolerance. These three factors combine into emergent phenomena, leading teams and organizations to act in ways no individual member would. The dissonance of how (personified) organizations behave confounds observers outside the bureaucracy. If you were to talk to each member, you could find a reason for that person's behavior. Individual bureaucrats do not act randomly.


% see https://en.wikipedia.org/wiki/Social_influence

Each bureaucrat has a motive, even the bureaucrats who do nothing. Bureaucratic nihilism (showing up for your job but choosing to not provide value) is an option, but it is not without cost.
% https://graphthinking.blogspot.com/2020/02/there-is-no-idle-status-for-paid.html
In an organization where you are a paid bureaucrat, you are either actively working to improve the organization or your existence is parasitic to the organization. There is no ``idle" status for paid employees in an organization with limited resources.

Employees may choose to stop contributing value if they perceive that a lack of action will not harm their options. There is a perceived disconnect between their actions and the consequences for the organization. This is not pure \href{https://en.wikipedia.org/wiki/Nihilism}{nihilism}, 
\index{Wikipedia!nihilism@\href{https://en.wikipedia.org/wiki/Nihilism}{nihilism}}
as the person still  benefits from showing up (usually a paycheck).

Rationalizing money as the cause for action is just one of many potential sources.
There are a variety of motivations and incentives for bureaucrats: 
stability (aka job security, the comfort of a routine),
money (current pay or future earnings), 
travel, 
problem-solving, 
social status, 
exerting power or control, 
the credibility of being associated with the organization (if the organization has a positive reputation), 
logistical convenience (``the office is near where I live''), 
service to people the organization serves.


As an example incentive for a bureaucrat, I want to avoid being too efficient such that I eliminate the need for my job, 
\marginpar{$>>$ \href{https://en.wikipedia.org/wiki/Goldilocks_principle}{Goldilocks balance}}%
while not so inefficient that the organization fails and I lose my job. Increasing the efficiency of bureaucracy is desirable for the organization and the outcomes, but can be harmful to the bureaucrat's career.


The consequence of diverse motives is that expecting bureaucratic organizations to be logical, fair, consistent, and efficient is unreasonable even when every participant wants those features. Each bureaucrat thinks, ``I am logical, fair, consistent, and efficient.'' Therefore each bureaucrat expects other bureaucrats to meet those same (unrealistic) standards. Next, anthropomorphize the team or organization and expect the group to meet those standards. 

Even if each bureaucrat were logical, fair, consistent, and efficient (they are not, and neither are you), each person has a different motivation. %Internal motivation depends on what you value in the sense of a
%\index{Wikipedia!\href{https://en.wikipedia.org/wiki/Utility}{utility}}
%\href{https://en.wikipedia.org/wiki/Utility}{utility}\iftoggle{WPinmargin}{\marginpar{$>$Wikipedia: Utility}}{}
%function.  
At the same time, each person wants to accomplish something using their skills. % and reference their own experiences. 
 Compounding the confusion, each bureaucrat has to coordinate using communication that has latency, limited bandwidth, and isn't precise.

When viewed from the outside, an expectation that bureaucracy feels illogical, unfair, inconsistent, and inefficient is a useful baseline. From inside the bureaucracy, a baseline expectation is that every bureaucrat is driven by different motives and uses distinct ways to tackle challenges. Working against bureaucratic entropy (an ongoing investment) yields improvements even though perfection is inaccessible.


\ \\

% TRANSITION to tropes

The above discussion might leave you with the impression that individual bureaucrats are distinct. While that's true, with a sufficient number of different people there are recurring themes that are detectable. The next section identifies common tropes you might encounter.