\section{Not Many Options for Organizations}
% https://graphthinking.blogspot.com/2021/07/patterns-anti-patterns-in-bureaucracy.html

The purpose of an organization or a team is to obfuscate the bureaucracy of enacting policies for managing access to shared resources. The value of organizations and teams is that they are a simplifying assumption that depersonalize the function of inputs and outputs. Without organizations or teams you would be directly exposed to the complexity of knowing every person's title and responsibility. Organizations and teams are abstractions to hide complexity.

When complaining about the ineptitude of organizations (or more specifically, leaders, managers, bureaucrats you manage, and coworkers), consider the variables available to be modified. As a thought exercise, what would it take to rebuild the organization you are in from scratch? 
\marginpar{$>>$ Thought Exercise}

Listing the levers available for enacting change in an organization is intended to emphasize the importance of personal interactions within bureaucracy. When you get frustrated with inefficiency, consider the systemic changes available -- there aren't that many. Options for restructuring the organization are limited, so the importance of your creativity and informal influence is dominant in determining the effectiveness of bureaucracy. Those factors relevant to Process Empathy are separate from having the right staff and being able to have an adequate number of staff. 

Organizations comprised of bureaucrats have fewer options for change than individual bureaucrats. The choices an individual bureaucrat faces are described
\iftoggle{haspagenumbers}{on page~\pageref{sec:dilemma-trilemma}}{ }%
 in the section on 
\hyperref[sec:dilemma-trilemma]{dilemmas}.
In comparison, the choices faced by the designers of an organization include:
\begin{itemize}
    \item Flatness of organizational hierarchy -- how many layers of oversight are there? Another way of arriving at the same structure is to ask how many employees there are per supervisor.
    \item Hierarchy split by function (all the lawyers in one team, all the engineers in one team, all the sales people in one team) or by product (mixing experts to solve a customer's problem)?

% https://graphthinking.blogspot.com/2023/07/matrixed-organizations-best-practices.html
    
    \item Size of organization. Having more people allows for more specialization and requires more support. 
    
    \item Organizations create processes for recurring tasks like hiring, promotion (pay or title), awards, compensation, recognition, professional training, and firing. Each of those has a set of design choices that inform the organization's culture.
\end{itemize}
In a government bureaucracy, the constraints of some incentives like pay and financial awards are set outside the organization. That further constrains the ability of bureaucrats to shape their organization's culture.

The organization may have policies and processes regarding hiring, promotion, training, and firing, but the decision may be made by team managers rather than top-level managers. 

%Listing how an organization could change is relevant 
Individual bureaucrats can enact change, and subjects of bureaucracy can request improvement, but those are weak inputs. 
Organizations are accountable to their source of funding, not the subjects of bureaucracy or members of the organization. For example, the \href{https://en.wikipedia.org/wiki/Internal_Revenue_Service}{Internal Revenue Service (IRS)} 
\index{exemplar!Internal Revenue Service@\href{https://en.wikipedia.org/wiki/Internal_Revenue_Service}{Internal Revenue Service}}
\index{Wikipedia!Internal Revenue Service@\href{https://en.wikipedia.org/wiki/Internal_Revenue_Service}{Internal Revenue Service}}%
is accountable to Congress, not taxpayers or IRS employees. 



A flat organization (more employees per manager) means more people doing work instead of managing, but sufficiently large organizations are typically broken into teams to make coordination less chaotic. 
%TODO:~\cite{2015_Katzenbach} (Wisdom of Teams book).


Organizations are segmented into teams and there are not many options: create a new team, merge existing teams, or dissolve a team. 


Shuffling the structure of teams (referred to as re-organization) is a favorite hobby of executive leadership. The alignment of hierarchical structure with an organization's purpose is a change that is easy to point to as an accomplishment. 


For a given set of teams, the lateral interactions are competitive or cooperative. Coordination is required (or conflict will occur) for money, staffing, and resources. Examples of resources include access to or control of data, computer equipment, hardware, floor space in a building, prestige, and ownership of products.

% ==== hierarchy - expand/contract ====
% Ways to expand and contract hierarchy as the number of employees in the workforce grows and shrinks
% * Add a new organization below: person who was an employee is now a manager and hires a bunch of people
% * Add a new peer team,
% * Add a new parent oversight organization above the current one
% * Unflatten an organization by inserting a new layer of management


Not all changes have to be structural; there are choices to be made when operating within the existing hierarchy.


\subsection*{Not Many Options Within Teams}



Similar to the limited number of options available for shaping organizations, the structural choices faced by a team are constrained. 


The purpose of pointing out the variables that can be changed is to show that there aren't many. As a consequence of the limited options, relationships and effective communication are more significant for effective bureaucracy. 


Team managers might decide who gets hired, who gets promoted, who goes to what training, and who gets fired. Though in some environments even that control is relegated to an external team. A team manager usually has decision-making authority regarding tasks the team works on. 

% intra- and inter- team dynamics

Accountability in the context of teams comes from person-to-person interactions. These can be either lateral (sideways), parent-child (top-down), or child-parent (bottom-up)~\cite{2014_Jorgensen}. Each of these three categories has associated constraints.

The upward child-parent (bottom-up) communication is either inadequate (too few updates, not enough information, or insufficient context), relevant, or excessive. For example, a weekly or monthly report to multiple superiors may be inadequate. 

Finding the balance depends on the presenter knowing the individual audience members so that a tailored message is provided and then adapting to the specifics of the situation. 
% tips on managing up: 
% https://svpg.com/managing-up/

The downward parent-child communication either is inadequate (no direction provided or imprecise direction provided), provides actionable vision, or micromanagement. Finding the right balance and specificity requires insight into the communication needs on both sides of the relationship. The manager of a team member has a variety of tools available beyond setting tasks and deadlines. A manager can create an environment that provides psychological safety, promotion based on accomplishments, recognition of contributions, encouragement, and constructive feedback.

For interactions among team members at the same hierarchical level the conflict of interests between cooperation and competition manifests in struggles over money, staffing, products (output), and resources (inputs). Here ``resources''  refers to constraints like access to data, control of data, technology resources, hardware, floor space, and expertise. 


% https://graphthinking.blogspot.com/2021/07/patterns-anti-patterns-in-bureaucracy.html

%\begin{itemize}
%    \item money
%    \item staffing
%    \item prestige
%    \item products (output)
%    \item resources (inputs)
%    \begin{itemize}
%        \item access to or control of data
%        \item technology resources
%        \item hardware
%        \item floor space
%        \item expertise
%    \end{itemize}
%\end{itemize}


Understanding the options available for organizations, teams, and relationships informs your Process Empathy. There are constraints bureaucrats operate within and there are a limited number of ways to evolve out of a situation. By listing possible ways to change you can identify which options are best to invest in. 