\section{Design of Processes\label{sec:design-of-processes}}


Bureaucracy is the use of distributed knowledge and distributed decision-making for policies concerning access to shared resources. A set of \iftoggle{glossarysubstitutionworks}{\glspl{process}}{processes}
\iftoggle{glossaryinmargin}{\marginpar{[Glossary]}}{} is used by \iftoggle{glossarysubstitutionworks}{\glspl{bureaucrat}}{bureaucrats} to leverage specialization and improve throughput. 
    
Because bureaucrats are typically not formally trained in designing processes, ad hoc ideas reactive to the immediate situation and local constraints are used. A thoughtful process designer tries to account for exceptions \iftoggle{haspagenumbers}{ (page~\pageref{sec:exceptions-to-process})}{} 
and potential mistakes\iftoggle{haspagenumbers}{ (page~\pageref{sec:process-mistakes}).}{.}

% https://graphthinking.blogspot.com/2016/04/if-you-want-boulder-to-roll-place-it-at.html
The most effective process is a minimal process.
When designing a process, look for ways to minimize the work for the people involved. Minimizing work (both physical and mental) for the people involved means less sensitivity to entropy in a bureaucracy. Minimizing work requires significant situational awareness on the part of the designer. To minimize the requirements to achieve success, minimizing the effect on existing bureaucracy is vital.

Another question to ask when designing a bureaucratic process is whether a process is needed. Can the goal be accomplished by relying on ad hoc responses and leveraging relationships among bureaucrats?
% https://graphthinking.blogspot.com/2021/04/laffer-curve-and-minimum-viable.html
There is a Goldilocks situation for the number of processes in an organization:
\marginpar{$>>$ \href{https://en.wikipedia.org/wiki/Goldilocks_principle}{Goldilocks balance}}
\index{Goldilocks balance!number of processes}
\begin{itemize}
    \item Too few processes (all social relationships). New participants, lacking necessary relationships, find the team or organization chaotic. 
    \item Just the right amount -- a balance of process and social relationships, and knowing when to use which. Each participant  has a different view about what the right balance is based on what relationships are accessible to them, and how burdensome they find a process. 
    \item Too much process (not enough leveraging of social relationships). When this happens, bureaucrats can end up resorting to the use of social relationships to circumvent burdensome processes.
\end{itemize}
This optimization is like the \href{https://en.wikipedia.org/wiki/Laffer_curve}{Laffer curve} in economics: there's a sweet-spot between the extremes.
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/Laffer_curve}{Laffer curve}}

Minimal processes and subtle change may not be available.
The following sections describe why static process designs are the norm, the role of bureaucratic debt, and how to design for turnover of staff.
    
\input{process_static_vs_dynamic}

\input{process_framing_bureaucratic_debt}

\input{process_design_processes_for_turnover} 