\iftoggle{narrowpage}{\section*{Two Page Summary of This Book}}{\section*{One Page Summary of This Book}}



\iftoggle{glossarysubstitutionworks}{\Gls{bureaucracy}}{Bureaucracy} is pervasive because it is crucial for society. 
Bureaucracy is defined by decisions originating from the 
management of access to \iftoggle{glossarysubstitutionworks}{\glspl{shared resource}.}{shared resources.} 
The resources can be either tangible or in the form of expertise. 
When there are multiple bureaucrats participating in an organization, 
\gls{decentralized bureaucracy} relies on distributed knowledge and distributed decision-making.


There are common artifacts that stem from the coordination necessary for bureaucracy: hierarchy (which enables specialization and decision authority) and communication -- verbal and written, whether for informal or formal meetings. 
%TODO: transition needed
Weak feedback loops are a crucial feature for understanding motives for decision-making in bureaucracy.
A policy defines what to do in a certain context -- how to make a decision. A process is the steps of enacting the policy.

Policies are typically intended to help all participants, both bureaucrats and subjects. The value of processes is that they are predictable. There's less cognitive load for bureaucrats and less emotional burden because ``I'm just following the rules.'' For subjects the value of a process is that requirements are clear and can be deemed fair in application. There's no need to form relationships with the people administering the shared resources.

The negative effect of a process can occur in both exceptional contexts and cases where relationships already exist. Then policies and processes get in the way.

Having both relationship-based and policy-based paradigms in effect at the same time is disruptive to each paradigm.  This inability of the two approaches (ad hoc versus systematic) to coexist is one reason why bureaucracy is consistently in turmoil. Therefore an effective bureaucrat learns to take advantage of the dynamics. Being a skilled bureaucrat involves 
forming and maintaining relationships with fellow bureaucrats and subjects,
comprehending and leveraging existing policies and processes, and 
disrupting existing processes with innovative policies.
%The wise bureaucrat knows when to employ which approach. 

%TODO: Bureaucracy book themes
%* Innoculation for dumb responses
%* I have a "new" idea (and why it won't work)
%* Labels matter for self-perception


%TODO: transition needed
\iftoggle{glossarysubstitutionworks}{\Gls{process empathy}}{Process empathy} 
is helpful in your role as a bureaucrat and when you are subject to bureaucracy. 
Process empathy is based on your understanding the \hyperref[sec:dilemma-trilemma]{dilemmas} and \hyperref[sec:unavoidable-hazards]{unavoidable hazards} of bureaucracy, recognizing internal 
\iftoggle{glossarysubstitutionworks}{\glspl{motive}}{motives} and external 
\iftoggle{glossarysubstitutionworks}{\glspl{incentive}}{incentives}
 that individuals in each role have, and your ability to reconstruct the sequence of decisions that led to the current situation. 


Innovation is stifled by bureaucracy%
\iftoggle{haspagenumbers}{ (see page~\pageref{sec:innovation})}{} because individual bureaucrats have incentive to adhere to existing policies and processes as a way to decrease their risk. Innovation requires adapting policies to new contexts and discarding irrelevant policies. 
The \hyperref[sec:extending-Heilmeier]{extended Heilmeier questions}%
\iftoggle{haspagenumbers}{ (see page~\pageref{sec:extending-Heilmeier})}{} can be used to interrogate the relevance of policies in a specific context.
%https://en.wikipedia.org/wiki/George_H._Heilmeier%23Heilmeier's_Catechism


Not all challenges you encounter as a bureaucrat in an organization are attributable to bureaucracy. The distribution of tasks in an organization lacking hierarchy can induce latency when not everyone has all relevant skills for 
\iftoggle{haspagenumbers}{tasks -- see page \pageref{sec:work-distribution}.}{tasks.}
Specialization of skills can improve task throughput when processes are stable, but specialization can hinder task throughput when task complexity requires coordination.

