% https://graphthinking.blogspot.com/2021/07/patterns-anti-patterns-in-bureaucracy.html

% intra- and inter- team dynamics

\subsection*{Teams are Subdivisions of an Organization}

A flat organization (more employees per manager) means more people doing work instead of managing, but sufficiently large organizations are typically broken into teams to make coordination less chaotic. 

%TODO:~\cite{2015_Katzenbach} (Wisdom of Teams book).

As a bureaucrat on a team, you might expect that there are structural ways to address challenges. 
In the context of altering teams, there are only a few options available: create a new team, merge teams, or dissolve a team. 

Not all changes have to be structural; there are choices to be made when operating within the existing hierarchy.
For a given set of teams, the lateral interactions are competitive or cooperative. Coordination is required (or conflict will occur) for money, staffing, and resources. Examples of resources include access to or control of data, computer equipment, hardware, floor space, prestige, and ownership of products.

The purpose of pointing out the variables that can be changed is that there aren't many. As a consequence, the importance of  relationships and effective communication is more significant. 

\subsection*{Roles of Management versus Leadership}

\index{mantra!management isn't leadership}
Teams include managers and leaders. Those roles are not necessarily filled by the same person. By clarifying the distinction, you can determine what to expect from various members of the hierarchy. A common mistake is to expect leadership from managers. 

A manager's role involves time management, task tracking, employee evaluations, promotion, pay, requesting resources for team members, and hiring. Sometimes the responsibilities of promotion, pay, and hiring are split into a supervisor role, leaving task tracking and time management to the project manager or product manager roles.

A leader's role focuses on coordinating vision and principles. The vision and principles do not have to originate from the leader -- other team members can contribute ideas. The leader's responsibility is primarily social consensus and aligning the goals of members. 
