\subsection{Tips for working as a bureaucrat in an organization}

Superpowers of a bureaucrat in a bureaucratic organization that facilitate cooperation and progress:
\begin{itemize}
    \item be more transparent
    \item make yourself accountable
    \item communicate more effectively
    \item Multi-tasking, or, more accurately, task switching. The switch among tasks is triggered when the current task encounters an externally-generated pause. \href{https://en.wikipedia.org/wiki/Pipeline_(computing)#Concept_and_motivation}{pipeline your activities}.
    \item Be prepared with a backlog of ideas (in writing) if someone shows up with resources.
    \item If you are dependent on someone else getting something done to enable your progress, \underline{presence creates priority}.
    \item Quickly replying to incoming requests. This allows other people's tasks to either be resolved or have a clear response about when progress can be expected. 
    \item intellectual empathy -- what is it; how to grow it. Theory of mind for thinking. shadow peers and bosses
    \item process empathy. Observe deviations and exceptions that cause processes to come into existence. 
    \item Avoid unintentionally dropping tasks or requests. This requires capturing incoming requests and then providing a response about prioritization and status. This matters because other participants in the organization should regard you as reliable in a positive sense. 
\end{itemize}

Bureaucracy induces emotional response in participants because things don't work they way each person wants. This can lead emotionally to frustration and then apathy. Understanding how things operate in a bureaucracy decreases the anger.

% Wandering the maze of bureaucratic processes as a subject.

Another emotional response to bureaucracy is a sense of powerlessness. 
\begin{quote}
Some third person decides your fate: this is the whole essence of bureaucracy.\footnote{``The Workers' Opposition'' by Alexandra Kollontai, 1921}
% https://alphahistory.com/russianrevolution/kollontai-on-soviet-bureaucracy-1921/
\end{quote}
That sense of powerlessness applies both to bureaucrats and to subjects of bureaucracy. 

The sense of powerlessness is somewhat valid, in that you are as a bureaucrat giving up some power compared to your ability to act individually. That is the trade for working with others

\ \\

A process feels bureaucratic when the subject is exposed to more than one step to get something done that if one person were doing it would be simpler. Consolidation from the subject's perspective decreases the apparent bureaucracy. The barrier to implementation is the necessary coordination among different stakeholders who receive no benefit from the coordination. Externalizing the coordination to the subject is what causes the sense of bureaucracy. 


\ \\

Don't rely on one person or one idea for your success. Don't spread yourself too thin. 

\ \\

what to do when you get stuck?
look up stream, look downstream, look to peers

\ \\

When you are asked to take on additional work, avoid responding with ``that's not my job." If the request is misguided and your perception is that is really is the responsibility of another person, ask if the requester is aware of that other person's responsibilities. If you are to really take on the work, get guidance on re-prioritizing and make sure the request is documented in writing. 

\ \\

If there's something you want to accomplish, strive for influence without authority instead of working to gain control over resources (e.g., through promotion). Avoid the following: ``In this organization X is important to me, but I can't do X right now because I don't have enough power in the org. So I'll get promoted and then do X."

\ \\

