\section{Bureaucratic Tropes\label{sec:tropes}}

Any sufficiently large organization will have a diverse group of bureaucrats. From that diversity certain tropes emerge.\footnote{J.~Duffy, personal communication, 2017.} The value of recognizing these recurring patterns is to leverage their strengths so that you and that person can be more effective. 


\begin{itemize}
    \item \textit{Trope}: \textbf{Excited intern or new employee}. \\
    \textit{What you can do}: Their enthusiasm can be channeled to take on challenges other bureaucrats are scared of taking on for political reasons. Their na\"ivet\'e 
    % https://en.wiktionary.org/wiki/na%C3%AFvet%C3%A9
    should be remedied by pairing them with a mentor who can explain the organization's history and specific challenges.
    
    \item \textit{Trope}: \textbf{Retired in place}. \\
    \textit{What you can do}: Recognizing this attitude allows you to temper your expectations about their productivity. 
    
    \item \textit{Trope}: \textbf{Font of institutional memory}. Likes to explain how the current situation relates to his experience ten years ago. \\
    \textit{What you can do}: You can benefit from talking to this person about historical processes and what has been tried before. 
    
    \item \textit{Trope}: \textbf{``Let them eat cake'' managers} who are removed from challenges and deny the problem is a problem. \\
    \textit{What you can do}: It is worth figuring out whether these managers actually don't care, or if they are busy fighting battles you are not exposed to.
    
    \item \textit{Trope}: \textbf{``Don't rock the boat''} people who tried changing the system, didn't succeed, and are emotionally beaten down such that they no longer try. \\
    \textit{What you can do}: These people are often creative and can be consulted before you tackle a challenge they have experience with. 
    
    \item \textit{Trope}: \textbf{The Patriot} is willing to sacrifice for the organization. \\
    \textit{What you can do}: Educate them that there are alternative ways to be effective in a bureaucracy.
    
    \item \textit{Trope}: \textbf{Mismatched} -- this person's skills and interests don't match their role, so they are despondent and frustrated. \\
    \textit{What you can do}: You can provide value to this person by networking with them and finding better opportunities.
    
    \item \textit{Trope}: \textbf{Friendly grouch} is friendly and helpful but unhappy in their job due to bureaucracy and other hurdles. \\
    \textit{What you can do}: Provide a copy of this book to increase their effectiveness and improve their spirits. They will be grateful to you and the organization will benefit.
    
    \item \textit{Trope}: \textbf{Detail-oriented} -- you ask them what time it is and they'll tell you how to build a clock. \\
    \textit{What you can do}: You can serve as their ambassador to other members of the team or organization.  
\end{itemize}


% see related but not relevant
% https://blog.codinghorror.com/which-online-discussion-archetype-are-you/
The above personality tropes apply to individuals. If your team works on multiple projects, you may identify project tropes:
\begin{itemize}
    \item \textit{Trope}: \textbf{We've always done it this way}.\\
    \textit{Assessment}: The team is scared of change. The change may be known (and undesirable) or unknown. Change disrupts power.\\
    \textit{What you can do}: You can brainstorm with the team ways to improve incrementally. 

    \item \textit{Trope}: \textbf{Individual solutions to systemic challenges}.\\
    \textit{Assessment}: Demonstrating small wins helps build credibility. \\
    \textit{What you can do}: Plan to ramp up  complexity (towards the systemic challenges) and \hyperref[sec:reputation]{spend the earned reputation}.
\marginpar{See page~\pageref{sec:reputation}.}
\end{itemize}
Team tropes can emerge from either the top-down directives made by supervisors or by the collective (in)actions of team members.


\ \\

% TRANSITION to solving_problems

Tropes as labeled patterns of behavior can decrease surprise when you first encounter them and can help you develop constructive responses. 

The last set of tropes is on the topic of bureaucratic problems. 