\section{Reader's Report\label{sec:reader-report}}
An view from inside bureaucracy as a \href{https://en.wikipedia.org/wiki/Complexity_theory_and_organizations}{complex adaptive system}, 
\index{Wikipedia!\href{https://en.wikipedia.org/wiki/Complexity_theory_and_organizations}{Complexity theory and organizations}}
with tips on how to be more effective. 

\ \\
Central claims made in this book:
\begin{itemize}
    \item Everyone in modern society takes part in \gls{bureaucracy}. Therefore learning to be a skilled \gls{bureaucrat} is useful.
    \item Individuals already have experience with bureaucracy from conventional roles in modern society. 
    \item Emergent behavior and being a \href{https://en.wikipedia.org/wiki/Wicked_problem}{wicked problem} 
    \index{Wikipedia!\href{https://en.wikipedia.org/wiki/Wicked_problem}{wicked problem}}
    make the complexity of bureaucracy irreducible to a simplistic model.
    \item The techniques of bureaucracy are meetings, processes, communication. These facilitate the coordination of distributed knowledge for distributed decision making.  
    \item Bureaucracy occurs when there is a lack of common quantitative feedback mechanism for individuals.
\end{itemize}
The consequences of thinking like a bureaucrat include
\begin{itemize}
    \item Applying \gls{process empathy} to better interact with coworkers and respond to complicated situations more effectively.
    \item You are not limited to only the direct personal interactions that you have with other people. Bureaucratic processes that exceed your direct visibility and experience extend your influence.
    \item Help you recognize options beyond the naive defaults associated with \hyperref[sec:fallacies]{fallacies}
    (see page~\pageref{sec:fallacies}). 
    What's feasible? What's negotiable? Once you realize rules and processes are subjectively created and enforced, negotiation (and identifying who to negotiate with) is more obvious.
    \item Decreased surprise when thing is not the way you naively expect. See the discussion of \hyperref[sec:dilemma-trilemma]{dilemmas}
    on page~\pageref{sec:dilemma-trilemma} 
    and 
    \hyperref[sec:unavoidable-hazards]{known hazards}
    on page~\pageref{sec:unavoidable-hazards}.
\end{itemize}


The effects of bureaucracy are not attributable to one person, but each person can improve bureaucracy.